---
title: "Rest of Draft Model"
author: "Anthony Rio"
date: "2023-11-29"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sophomore Model
```{r, include=FALSE, warning=FALSE}
library(stringr)
library(DT)
library(tidyverse)
train_data <- read.csv("Sophomore_Game_Data.csv")
head(train_data)

colnames(train_data)[c(6, 32, 35)] <- c("MIN", "X2PM", "X3PM")

# fix CONF
for (i in 1:nrow(train_data)) {
  if (train_data$CONF[i] == "ACC" | train_data$CONF[i] == "B12" | train_data$CONF[i] == "P12" | train_data$CONF[i] == "SEC" | train_data$CONF[i] == "B10" | train_data$CONF[i] == "BE") {
    train_data$CONF[i] <- 1
    } else {
      train_data$CONF[i] <- 0
    }
}
train_data$CONF <- as.numeric(train_data$CONF)


#fix height
for (i in 1:nrow(train_data)) {
  train_data$Height[i] <- as.numeric(str_split(train_data$Height[i], "-")[[1]][1]) * 12 + as.numeric(str_split(train_data$Height[i], "-")[[1]][2])
}



colnames(train_data)
#Fix Dunks, C2M, FTM, F2M, 2PM., X3PM.
for (i in 1:nrow(train_data)) {
  train_data$Dunks[i] <- as.numeric(str_split(train_data$Dunks[i], "-")[[1]][1])
  train_data$C2M[i] <- as.numeric(str_split(train_data$C2M[i], "-")[[1]][1])
  train_data$FTM[i] <- as.numeric(str_split(train_data$FTM[i], "-")[[1]][1])
  train_data$F2M[i] <- as.numeric(str_split(train_data$F2M[i], "-")[[1]][1])
  train_data$X2PM[i] <- as.numeric(str_split(train_data$X2PM[i], "-")[[1]][1])
  train_data$X3PM[i] <- as.numeric(str_split(train_data$X3PM[i], "-")[[1]][1])
}


#fix drafted
train_data$drafted <- train_data$Pick

for (i in 1:nrow(train_data)) {
  if (train_data$drafted[i] == "-") {
    train_data$drafted[i] <- 0
  } else {
    train_data$drafted[i] <- 1
  }
}
train_data$drafted <- as.numeric(train_data$drafted)
train_data$Height <- as.numeric(train_data$Height)
train_data$Dunks <- as.numeric(train_data$Dunks)
train_data$C2M <- as.numeric(train_data$C2M)
train_data$F2M <- as.numeric(train_data$F2M)
train_data$FTM <- as.numeric(train_data$FTM)
train_data$X2PM <- as.numeric(train_data$X2PM)
train_data$X3PM <- as.numeric(train_data$X3PM)
train_data$C2P <- as.numeric(train_data$C2P)
train_data$F2P <- as.numeric(train_data$F2P)
train_data$FTP <- as.numeric(train_data$FTP)
train_data$X2PP <- as.numeric(train_data$X2PP)
train_data$X3PP <- as.numeric(train_data$X3PP)
train_data$X3PR <- as.numeric(train_data$X3PR)

train_data$Dunks <- train_data$Dunks * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$C2M <- train_data$C2M * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$F2M <- train_data$F2M * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$FTM <- train_data$FTM * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$X2PM <- train_data$X2PM * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$X3PM <- train_data$X3PM * 40 / (train_data$MIN / 100 * train_data$Games * 40)
```

### Train Model
```{r}
log_model <- glm(drafted ~ Height + CONF + MIN + PRPG + DPRPG + BPM + OBPM + DBPM + ORTG + D.RTG + USG + EFG + TS + FC + OR + DR + AST + TO + BLK + STL + FTR + C2P + F2P + FTP + X2PP + X3PR + X3PP + Dunks + F2M + C2M + X3PM + FTM + X2PM, data = train_data, family = "binomial")
```

### Prepare 2023 Data
```{r, include=FALSE, include=FALSE}
test_data <- read.csv("Sophomore_2024_Data.csv")

colnames(test_data)[c(3, 31, 34)] <- c("CONF", "X2PM", "X3PM")


#fix CONF
for (i in 1:nrow(test_data)) {
  if (test_data$CONF[i] == "ACC" | test_data$CONF[i] == "B12" | test_data$CONF[i] == "P12" | test_data$CONF[i] == "SEC" | test_data$CONF[i] == "B10" | test_data$CONF[i] == "BE") {
    test_data$CONF[i] <- 1
    } else {
      test_data$CONF[i] <- 0
    }
}
test_data$CONF <- as.numeric(test_data$CONF)



#fix height
for (i in 1:nrow(test_data)) {
  test_data$Height[i] <- as.numeric(str_split(test_data$Height[i], "-")[[1]][1]) * 12 + as.numeric(str_split(test_data$Height[i], "-")[[1]][2])
}


#Fix Dunks, C2M, FTM, F2M, 2PM., X3PM.
for (i in 1:nrow(test_data)) {
  test_data$Dunks[i] <- as.numeric(str_split(test_data$Dunks[i], "-")[[1]][1])
  test_data$C2M[i] <- as.numeric(str_split(test_data$C2M[i], "-")[[1]][1])
  test_data$FTM[i] <- as.numeric(str_split(test_data$FTM[i], "-")[[1]][1])
  test_data$F2M[i] <- as.numeric(str_split(test_data$F2M[i], "-")[[1]][1])
  test_data$X2PM[i] <- as.numeric(str_split(test_data$X2PM[i], "-")[[1]][1])
  test_data$X3PM[i] <- as.numeric(str_split(test_data$X3PM[i], "-")[[1]][1])
}

test_data$Height <- as.numeric(test_data$Height)
test_data$Dunks <- as.numeric(test_data$Dunks)
test_data$C2M <- as.numeric(test_data$C2M)
test_data$F2M <- as.numeric(test_data$F2M)
test_data$FTM <- as.numeric(test_data$FTM)
test_data$X2PM <- as.numeric(test_data$X2PM)
test_data$X3PM <- as.numeric(test_data$X3PM)

test_data$Dunks <- test_data$Dunks * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$C2M <- test_data$C2M * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$F2M <- test_data$F2M * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$FTM <- test_data$FTM * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$X2PM <- test_data$X2PM * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$X3PM <- test_data$X3PM * 40 / (test_data$MIN / 100 * test_data$Games * 40)


test_data$C2P <- as.numeric(test_data$C2P)
test_data$F2P <- as.numeric(test_data$F2P)
test_data$FTP <- as.numeric(test_data$FTP)
test_data$X2PP <- as.numeric(test_data$X2PP)
test_data$X3PP <- as.numeric(test_data$X3PP)
test_data$X3PR <- as.numeric(test_data$X3PR)

X_test <- test_data[ , c('Height', 'CONF', 'MIN', 'PRPG', 'DPRPG', 'BPM', 'OBPM', 'DBPM', 'ORTG', 'D.RTG', 'USG', 'EFG', 'TS', 'FC', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'F2P', 'FTP', 'X2PP', 'X3PR', 'X3PP', 'Dunks', 'F2M', 'C2M', 'X3PM', 'FTM', 'X2PM')]

#X_test <- test_data[ , c('Height', 'CONF', 'MIN.', 'USG', 'TS', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'X3P', 'X3PP', 'Dunks', 'C2M')]


# X_train <- train_data[ , c('Height', 'CONF', 'MIN', 'PRPG', 'DPRPG', 'BPM', 'OBPM', 'DBPM', 'ORTG', 'D.RTG', 'USG', 'EFG', 'TS', 'FC', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'F2P', 'FTP', 'X2PP', 'X3PR', 'X3PP', 'Dunks', 'F2M', 'C2M', 'X3PM', 'FTM', 'X2PM')]

# Y_train <- train_data[ , 'drafted']
```

### Make Predictions
```{r, include=FALSE}
result <- data.frame("Player" = test_data$Player, "Prediction" = as.numeric(predict(log_model, X_test, type = "response") > 0.5))

#predict(log_model, X_test, type = "response")

drafted <- result[result$Prediction == 1, ]

result_raw <- data.frame("Player" = test_data$Player, "Raw_Prediction" = predict(log_model, X_test, type = "response"))

just_missed <- result_raw %>% filter(Raw_Prediction > 0.2 & Raw_Prediction < 0.5)

raw <- result_raw %>% arrange(desc(Raw_Prediction)) %>% head(50)
```

## Sophomores Predicted To Be Drafted:
```{r}
datatable(drafted)
```

## Sophomores Who Just Missed the Cut:
```{r}
datatable(just_missed)
```


# Junior Model
```{r, include=FALSE, warning=FALSE}
train_data <- read.csv("Junior_Game_Data.csv")
head(train_data)

colnames(train_data)[c(6, 32, 35)] <- c("MIN", "X2PM", "X3PM")

# fix CONF
for (i in 1:nrow(train_data)) {
  if (train_data$CONF[i] == "ACC" | train_data$CONF[i] == "B12" | train_data$CONF[i] == "P12" | train_data$CONF[i] == "SEC" | train_data$CONF[i] == "B10" | train_data$CONF[i] == "BE") {
    train_data$CONF[i] <- 1
    } else {
      train_data$CONF[i] <- 0
    }
}
train_data$CONF <- as.numeric(train_data$CONF)


#fix height
for (i in 1:nrow(train_data)) {
  train_data$Height[i] <- as.numeric(str_split(train_data$Height[i], "-")[[1]][1]) * 12 + as.numeric(str_split(train_data$Height[i], "-")[[1]][2])
}



colnames(train_data)
#Fix Dunks, C2M, FTM, F2M, 2PM., X3PM.
for (i in 1:nrow(train_data)) {
  train_data$Dunks[i] <- as.numeric(str_split(train_data$Dunks[i], "-")[[1]][1])
  train_data$C2M[i] <- as.numeric(str_split(train_data$C2M[i], "-")[[1]][1])
  train_data$FTM[i] <- as.numeric(str_split(train_data$FTM[i], "-")[[1]][1])
  train_data$F2M[i] <- as.numeric(str_split(train_data$F2M[i], "-")[[1]][1])
  train_data$X2PM[i] <- as.numeric(str_split(train_data$X2PM[i], "-")[[1]][1])
  train_data$X3PM[i] <- as.numeric(str_split(train_data$X3PM[i], "-")[[1]][1])
}


#fix drafted
train_data$drafted <- train_data$Pick

for (i in 1:nrow(train_data)) {
  if (train_data$drafted[i] == "-") {
    train_data$drafted[i] <- 0
  } else {
    train_data$drafted[i] <- 1
  }
}
train_data$drafted <- as.numeric(train_data$drafted)
train_data$Height <- as.numeric(train_data$Height)
train_data$Dunks <- as.numeric(train_data$Dunks)
train_data$C2M <- as.numeric(train_data$C2M)
train_data$F2M <- as.numeric(train_data$F2M)
train_data$FTM <- as.numeric(train_data$FTM)
train_data$X2PM <- as.numeric(train_data$X2PM)
train_data$X3PM <- as.numeric(train_data$X3PM)
train_data$C2P <- as.numeric(train_data$C2P)
train_data$F2P <- as.numeric(train_data$F2P)
train_data$FTP <- as.numeric(train_data$FTP)
train_data$X2PP <- as.numeric(train_data$X2PP)
train_data$X3PP <- as.numeric(train_data$X3PP)
train_data$X3PR <- as.numeric(train_data$X3PR)

train_data$Dunks <- train_data$Dunks * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$C2M <- train_data$C2M * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$F2M <- train_data$F2M * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$FTM <- train_data$FTM * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$X2PM <- train_data$X2PM * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$X3PM <- train_data$X3PM * 40 / (train_data$MIN / 100 * train_data$Games * 40)



log_model <- glm(drafted ~ Height + CONF + MIN + PRPG + DPRPG + BPM + OBPM + DBPM + ORTG + D.RTG + USG + EFG + TS + FC + OR + DR + AST + TO + BLK + STL + FTR + C2P + F2P + FTP + X2PP + X3PR + X3PP + Dunks + F2M + C2M + X3PM + FTM + X2PM, data = train_data, family = "binomial")
```


```{r, include=FALSE, warning=FALSE}
test_data <- read.csv("Junior_2024_Data.csv")

colnames(test_data)[c(3, 31, 34)] <- c("CONF", "X2PM", "X3PM")


#fix CONF
for (i in 1:nrow(test_data)) {
  if (test_data$CONF[i] == "ACC" | test_data$CONF[i] == "B12" | test_data$CONF[i] == "P12" | test_data$CONF[i] == "SEC" | test_data$CONF[i] == "B10" | test_data$CONF[i] == "BE") {
    test_data$CONF[i] <- 1
    } else {
      test_data$CONF[i] <- 0
    }
}
test_data$CONF <- as.numeric(test_data$CONF)



#fix height
for (i in 1:nrow(test_data)) {
  test_data$Height[i] <- as.numeric(str_split(test_data$Height[i], "-")[[1]][1]) * 12 + as.numeric(str_split(test_data$Height[i], "-")[[1]][2])
}


#Fix Dunks, C2M, FTM, F2M, 2PM., X3PM.
for (i in 1:nrow(test_data)) {
  test_data$Dunks[i] <- as.numeric(str_split(test_data$Dunks[i], "-")[[1]][1])
  test_data$C2M[i] <- as.numeric(str_split(test_data$C2M[i], "-")[[1]][1])
  test_data$FTM[i] <- as.numeric(str_split(test_data$FTM[i], "-")[[1]][1])
  test_data$F2M[i] <- as.numeric(str_split(test_data$F2M[i], "-")[[1]][1])
  test_data$X2PM[i] <- as.numeric(str_split(test_data$X2PM[i], "-")[[1]][1])
  test_data$X3PM[i] <- as.numeric(str_split(test_data$X3PM[i], "-")[[1]][1])
}

test_data$Height <- as.numeric(test_data$Height)
test_data$Dunks <- as.numeric(test_data$Dunks)
test_data$C2M <- as.numeric(test_data$C2M)
test_data$F2M <- as.numeric(test_data$F2M)
test_data$FTM <- as.numeric(test_data$FTM)
test_data$X2PM <- as.numeric(test_data$X2PM)
test_data$X3PM <- as.numeric(test_data$X3PM)

test_data$Dunks <- test_data$Dunks * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$C2M <- test_data$C2M * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$F2M <- test_data$F2M * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$FTM <- test_data$FTM * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$X2PM <- test_data$X2PM * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$X3PM <- test_data$X3PM * 40 / (test_data$MIN / 100 * test_data$Games * 40)


test_data$C2P <- as.numeric(test_data$C2P)
test_data$F2P <- as.numeric(test_data$F2P)
test_data$FTP <- as.numeric(test_data$FTP)
test_data$X2PP <- as.numeric(test_data$X2PP)
test_data$X3PP <- as.numeric(test_data$X3PP)
test_data$X3PR <- as.numeric(test_data$X3PR)


#write.csv(test_data, "~/Desktop/R_Projects/draft_test_data.csv")
X_test <- test_data[ , c('Height', 'CONF', 'MIN', 'PRPG', 'DPRPG', 'BPM', 'OBPM', 'DBPM', 'ORTG', 'D.RTG', 'USG', 'EFG', 'TS', 'FC', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'F2P', 'FTP', 'X2PP', 'X3PR', 'X3PP', 'Dunks', 'F2M', 'C2M', 'X3PM', 'FTM', 'X2PM')]

#X_test <- test_data[ , c('Height', 'CONF', 'MIN.', 'USG', 'TS', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'X3P', 'X3PP', 'Dunks', 'C2M')]


# X_train <- train_data[ , c('Height', 'CONF', 'MIN', 'PRPG', 'DPRPG', 'BPM', 'OBPM', 'DBPM', 'ORTG', 'D.RTG', 'USG', 'EFG', 'TS', 'FC', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'F2P', 'FTP', 'X2PP', 'X3PR', 'X3PP', 'Dunks', 'F2M', 'C2M', 'X3PM', 'FTM', 'X2PM')]

# Y_train <- train_data[ , 'drafted']
```


```{r, include=FALSE}
result <- data.frame("Player" = test_data$Player, "Prediction" = as.numeric(predict(log_model, X_test, type = "response") > 0.5))

#predict(log_model, X_test, type = "response")

drafted <- result[result$Prediction == 1, ]

result_raw <- data.frame("Player" = test_data$Player, "Raw_Prediction" = predict(log_model, X_test, type = "response"))

just_missed <- result_raw %>% filter(Raw_Prediction > 0.2 & Raw_Prediction < 0.5)

raw <- result_raw %>% arrange(desc(Raw_Prediction)) %>% head(50)
```

## Juniors Predicted To Be Drafted:
```{r}
datatable(drafted)
```

## Juniors Who Just Missed the Cut:
```{r}
datatable(just_missed)
```

# Senior Model

### Note: This model seemed the worst just based on its prediction output and high number of projected senior draftees. 

```{r, include=FALSE, warning=FALSE}
train_data <- read.csv("Senior_Game_Data.csv")
head(train_data)

colnames(train_data)[c(6, 32, 35)] <- c("MIN", "X2PM", "X3PM")

# fix CONF
for (i in 1:nrow(train_data)) {
  if (train_data$CONF[i] == "ACC" | train_data$CONF[i] == "B12" | train_data$CONF[i] == "P12" | train_data$CONF[i] == "SEC" | train_data$CONF[i] == "B10" | train_data$CONF[i] == "BE") {
    train_data$CONF[i] <- 1
    } else {
      train_data$CONF[i] <- 0
    }
}
train_data$CONF <- as.numeric(train_data$CONF)


#fix height
for (i in 1:nrow(train_data)) {
  train_data$Height[i] <- as.numeric(str_split(train_data$Height[i], "-")[[1]][1]) * 12 + as.numeric(str_split(train_data$Height[i], "-")[[1]][2])
}



colnames(train_data)
#Fix Dunks, C2M, FTM, F2M, 2PM., X3PM.
for (i in 1:nrow(train_data)) {
  train_data$Dunks[i] <- as.numeric(str_split(train_data$Dunks[i], "-")[[1]][1])
  train_data$C2M[i] <- as.numeric(str_split(train_data$C2M[i], "-")[[1]][1])
  train_data$FTM[i] <- as.numeric(str_split(train_data$FTM[i], "-")[[1]][1])
  train_data$F2M[i] <- as.numeric(str_split(train_data$F2M[i], "-")[[1]][1])
  train_data$X2PM[i] <- as.numeric(str_split(train_data$X2PM[i], "-")[[1]][1])
  train_data$X3PM[i] <- as.numeric(str_split(train_data$X3PM[i], "-")[[1]][1])
}


#fix drafted
train_data$drafted <- train_data$Pick

for (i in 1:nrow(train_data)) {
  if (train_data$drafted[i] == "-") {
    train_data$drafted[i] <- 0
  } else {
    train_data$drafted[i] <- 1
  }
}
train_data$drafted <- as.numeric(train_data$drafted)
train_data$Height <- as.numeric(train_data$Height)
train_data$Dunks <- as.numeric(train_data$Dunks)
train_data$C2M <- as.numeric(train_data$C2M)
train_data$F2M <- as.numeric(train_data$F2M)
train_data$FTM <- as.numeric(train_data$FTM)
train_data$X2PM <- as.numeric(train_data$X2PM)
train_data$X3PM <- as.numeric(train_data$X3PM)
train_data$C2P <- as.numeric(train_data$C2P)
train_data$F2P <- as.numeric(train_data$F2P)
train_data$FTP <- as.numeric(train_data$FTP)
train_data$X2PP <- as.numeric(train_data$X2PP)
train_data$X3PP <- as.numeric(train_data$X3PP)
train_data$X3PR <- as.numeric(train_data$X3PR)

train_data$Dunks <- train_data$Dunks * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$C2M <- train_data$C2M * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$F2M <- train_data$F2M * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$FTM <- train_data$FTM * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$X2PM <- train_data$X2PM * 40 / (train_data$MIN / 100 * train_data$Games * 40)
train_data$X3PM <- train_data$X3PM * 40 / (train_data$MIN / 100 * train_data$Games * 40)



log_model <- glm(drafted ~ Height + CONF + MIN + PRPG + DPRPG + BPM + OBPM + DBPM + ORTG + D.RTG + USG + EFG + TS + FC + OR + DR + AST + TO + BLK + STL + FTR + C2P + F2P + FTP + X2PP + X3PR + X3PP + Dunks + F2M + C2M + X3PM + FTM + X2PM, data = train_data, family = "binomial")
```

```{r, include=FALSE, warning=FALSE}

test_data <- read.csv("Senior_2024_Data.csv")

colnames(test_data)[c(3, 31, 34)] <- c("CONF", "X2PM", "X3PM")


#fix CONF
for (i in 1:nrow(test_data)) {
  if (test_data$CONF[i] == "ACC" | test_data$CONF[i] == "B12" | test_data$CONF[i] == "P12" | test_data$CONF[i] == "SEC" | test_data$CONF[i] == "B10" | test_data$CONF[i] == "BE") {
    test_data$CONF[i] <- 1
    } else {
      test_data$CONF[i] <- 0
    }
}
test_data$CONF <- as.numeric(test_data$CONF)



#fix height
for (i in 1:nrow(test_data)) {
  test_data$Height[i] <- as.numeric(str_split(test_data$Height[i], "-")[[1]][1]) * 12 + as.numeric(str_split(test_data$Height[i], "-")[[1]][2])
}


#Fix Dunks, C2M, FTM, F2M, 2PM., X3PM.
for (i in 1:nrow(test_data)) {
  test_data$Dunks[i] <- as.numeric(str_split(test_data$Dunks[i], "-")[[1]][1])
  test_data$C2M[i] <- as.numeric(str_split(test_data$C2M[i], "-")[[1]][1])
  test_data$FTM[i] <- as.numeric(str_split(test_data$FTM[i], "-")[[1]][1])
  test_data$F2M[i] <- as.numeric(str_split(test_data$F2M[i], "-")[[1]][1])
  test_data$X2PM[i] <- as.numeric(str_split(test_data$X2PM[i], "-")[[1]][1])
  test_data$X3PM[i] <- as.numeric(str_split(test_data$X3PM[i], "-")[[1]][1])
}

test_data$Height <- as.numeric(test_data$Height)
test_data$Dunks <- as.numeric(test_data$Dunks)
test_data$C2M <- as.numeric(test_data$C2M)
test_data$F2M <- as.numeric(test_data$F2M)
test_data$FTM <- as.numeric(test_data$FTM)
test_data$X2PM <- as.numeric(test_data$X2PM)
test_data$X3PM <- as.numeric(test_data$X3PM)

test_data$Dunks <- test_data$Dunks * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$C2M <- test_data$C2M * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$F2M <- test_data$F2M * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$FTM <- test_data$FTM * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$X2PM <- test_data$X2PM * 40 / (test_data$MIN / 100 * test_data$Games * 40)
test_data$X3PM <- test_data$X3PM * 40 / (test_data$MIN / 100 * test_data$Games * 40)


test_data$C2P <- as.numeric(test_data$C2P)
test_data$F2P <- as.numeric(test_data$F2P)
test_data$FTP <- as.numeric(test_data$FTP)
test_data$X2PP <- as.numeric(test_data$X2PP)
test_data$X3PP <- as.numeric(test_data$X3PP)
test_data$X3PR <- as.numeric(test_data$X3PR)


#write.csv(test_data, "~/Desktop/R_Projects/draft_test_data.csv")
X_test <- test_data[ , c('Height', 'CONF', 'MIN', 'PRPG', 'DPRPG', 'BPM', 'OBPM', 'DBPM', 'ORTG', 'D.RTG', 'USG', 'EFG', 'TS', 'FC', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'F2P', 'FTP', 'X2PP', 'X3PR', 'X3PP', 'Dunks', 'F2M', 'C2M', 'X3PM', 'FTM', 'X2PM')]

#X_test <- test_data[ , c('Height', 'CONF', 'MIN.', 'USG', 'TS', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'X3P', 'X3PP', 'Dunks', 'C2M')]


# X_train <- train_data[ , c('Height', 'CONF', 'MIN', 'PRPG', 'DPRPG', 'BPM', 'OBPM', 'DBPM', 'ORTG', 'D.RTG', 'USG', 'EFG', 'TS', 'FC', 'OR', 'DR', 'AST', 'TO', 'BLK', 'STL', 'FTR', 'C2P', 'F2P', 'FTP', 'X2PP', 'X3PR', 'X3PP', 'Dunks', 'F2M', 'C2M', 'X3PM', 'FTM', 'X2PM')]

# Y_train <- train_data[ , 'drafted']
```


```{r, include=FALSE}
result <- data.frame("Player" = test_data$Player, "Prediction" = as.numeric(predict(log_model, X_test, type = "response") > 0.5))

#predict(log_model, X_test, type = "response")

drafted <- result[result$Prediction == 1, ]

result_raw <- data.frame("Player" = test_data$Player, "Raw_Prediction" = predict(log_model, X_test, type = "response"))

just_missed <- result_raw %>% filter(Raw_Prediction > 0.2 & Raw_Prediction < 0.5)

raw <- result_raw %>% arrange(desc(Raw_Prediction)) %>% head(50)
```

## Seniors Predicted To Be Drafted:
```{r}
datatable(drafted)
```

## Seniors Who Just Missed the Cut:
```{r}
datatable(just_missed)
```
